How Diverse is the MoMA: While Modern, Not Diverse in Its Artists and Directors

### 2023-04-06 outputs/paper/paper.qmd
Added discussion headers to outline of final paper

# Bar graph showing nationality distribution of constituents MoMA exhibits
cleaned_momaexhibit_data |>
  ggplot(mapping = aes(x = Nationality)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Nationality", y = "Count of Constituents in MoMA Exhibits") 
```

```{r}
#| label: fig-artistgender
#| fig-cap: Gender Distribution of Consituents (Artists, Staff) in MoMA Exhibits
#| echo: false

# Bar graph showing gender distribution of constituents MoMA exhibits
cleaned_momaexhibit_data |> count(Gender) |>
  ggplot(mapping = aes(x = Gender, y = n)) +
  geom_col() + 
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  labs(x = "Gender", y = "Count of Constituents in MoMA Exhibits") 
```

Investigating directors and department heads:
```{r}
#| label: fig-staffnationality
#| fig-cap: Nationality Distribution of Directors and Department Heads in MoMA
#| echo: false

# Bar graph showing nationality distribution of MoMA directors and department heads 
cleaned_momadirectors_data |>
  ggplot(mapping = aes(x = Nationality)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Nationality", y = "Count of MoMA Directors and Department Heads") 
```

```{r}
#| label: fig-staffgender
#| fig-cap: Gender Distribution of Directors and Department Heads in MoMA
#| echo: false

# Bar graph showing gender distribution of MoMA directors and department heads 
cleaned_momadirectors_data |>
  ggplot(mapping = aes(x = Gender)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Gender", y = "Count of MoMA Directors and Department Heads")
```

# Model

@@

# Discussion
## First discussion point {#sec-first-point}

>>>>

# Bar graph showing nationality distribution of constituents MoMA exhibits
cleaned_momaexhibit_data |>
  ggplot(mapping = aes(x = Nationality)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Nationality", y = "Count of Constituents in MoMA Exhibits") 
```
\newpage
```{r}
#| label: fig-artistgender
#| fig-cap: Gender Distribution of Consituents (Artists, Staff) in MoMA Exhibits
#| echo: false

# Bar graph showing gender distribution of constituents MoMA exhibits
cleaned_momaexhibit_data |> count(Gender) |>
  ggplot(mapping = aes(x = Gender, y = n)) +
  geom_col() + 
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  labs(x = "Gender", y = "Count of Constituents in MoMA Exhibits") 
```
\newpage
Investigating directors and department heads:
```{r}
#| label: fig-staffnationality
#| fig-cap: Nationality Distribution of Directors and Department Heads in MoMA
#| echo: false

# Bar graph showing nationality distribution of MoMA directors and department heads 
cleaned_momadirectors_data |>
  ggplot(mapping = aes(x = Nationality)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Nationality", y = "Count of MoMA Directors and Department Heads") 
```
\newpage
```{r}
#| label: fig-staffgender
#| fig-cap: Gender Distribution of Directors and Department Heads in MoMA
#| echo: false

# Bar graph showing gender distribution of MoMA directors and department heads 
cleaned_momadirectors_data |>
  ggplot(mapping = aes(x = Gender)) +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  geom_bar(position = "dodge2")+
  labs(x = "Gender", y = "Count of MoMA Directors and Department Heads")
```
\newpage
# Model

@@

# Discussion
## Gender distribition {#sec-first-point}
## Nationality distribition {#sec-second-point}
## Analyzing the model: is time a factor? {#sec-third-point}
## Comparing artists vs directors {#sec-fourth-point}
